### 2016-03-11 docs/ms_communitySynchrony.Rmd
adds pba edits to ms

\begin{abstract}
Temporal asynchrony among species is an important mechanism through which diversity can stabilize ecosystem function, but elucidating the mechanisms underlying species synchrony remains a challenge.
Here, we extend theory to predict species synchrony under limiting cases that we couple with an empirical analysis from five plant communities.
When parameterized with empirical estimates, our prediction of species synchrony under only environmental stochasticity best predicts observed synchrony of per capita growth rates.
In model simulations, average synchrony of per capita growth rates, which ranges from 0 (perfect asynchrony) to 1 (perfect synchrony), was higher when environmental variation was present (0.62) rather than absent (0.43).
Removing interspecific competition and demographic stochasticity had small effects on synchrony.
Our results suggest that all five communities represent the theoretical limiting case where demographic stochasticity and competition are weak, and community-wide synchrony can be predicted by the synchrony of species' environmental responses.
\end{abstract}

@@

INTRODUCTION
------------
The earth's ecosystems are in a period of rapid change due to species extinctions [@Cardinale2012], changes in community composition [@Dornelas2014a; @Vellend2013], and human-driven changes in the abiotic environment [@Vitousek1997].
Such changes can have profound impacts on the provisioning and stability of ecosystem services [@Loreau2001a; @Hooper2005; @Rockstrom2009].
In particular, studies of experimental grassland communities show that greater species richness leads to greater productivity [@Tilman2001] and temporal stability of productivity [@Tilman2006; @Hector2010].
The stabilizing effect of species richness stems from individual species fluctuating asynchronously through time [@Hector2010; @Isbell2009; @DeMazancourt2013a].
Species richness affects synchrony because larger species pools are more likely to contain species that respond disimilarly to environmental conditions [@Yachi1999], which implies that species losses will reduce ecosystem stability.
Even without species losses, abiotic homogenization can weaken compensatory dynamics and, in turn, decrease temporal stability of ecosystem function [@Hautier2014].
Thus, it is becoming clear that predicting the impacts of global change requires a mechanistic understanding of species synchrony in natural settings.

Theory identifies the three main determinants of species synchrony as environmental stochasticity, demographic stochasticity, and interspecific competition [@Loreau2008a; @Gonzalez2009; @Loreau2013].
For example, in a community composed of large (no demographic stochasticity) and weakly interacting (no interspecific competition) populations, community-wide species synchrony should be determined by the covariance of species' responses to the environment [@Loreau2008a].
However, such a prediction relies on a relatively simple population dynamical model and only holds under two assumptions: (i) species' responses to the environment are similar in magnitude and (ii) that all species have similar growth rates.
Whether such theoretical predictions hold in natural communities where species differences are unlikely to be symmetrical remains unkown.
Indeed, no study has explicitly tested theory on the drivers of species synchrony in natural communities.

@@

The best way to quantify the effects of environmental stochasticity, demographic stochasticity, and interspecific competition is to remove them one-by-one, and in combination.
This could be done experimentally, but empirically-based models of interacting populations offer a way to exploit existing data sets from natural communities.
For example, @Mutshinda2009 fit a dynamic population model to several community time series of insect and bird abundances.
They used a statistical technique to decompose temporal variation into competition and environmental components, and found that postively correlated environmental responses among species determined community dynamics.
While a major step forward, Mutshinda et al.'s (2009) modeling technique relied on abundance data that may or may not reliably capture competitive interactions that occur at the individual level.
Furthermore, although @Mutshinda2009 quantify the relative importance of environmental stochasticity and competition to explain the observed variation of species synchrony, they did not use the model to quantify how much synchrony changes when each factor is removed.

Here, we use multi-species population models fit to long-term demographic data from five semi-arid plant communities to test theory on the drivers of species synchrony.
Our objectives are to (1) derive and test theoretical predictions of species synchrony and (2) determine the relative influence of environmental stochasticity, demographic stochasticity, and interspecific competition on species synchrony in natural plant communities.
To achieve these objectives, we first refine theory that has been used to predict the effects of species richness on ecosystem stability [@DeMazancourt2013a] and species synchrony [@Loreau2008a] to generate predictions of community-wide species synchrony under two limiting cases derived from the dynamics of individual species in monoculture.
We then confront our theoretical predictions with data from five semi-arid plant communities by using empirically-based population models.
Second, we use the multi-species population models to perform simulation experiments designed to isolate the effects of environmental stochasticity, demographic stochasticity, and interspecific competition on community-wide species synchrony.
Given that our population models capture the essential features of community dynamics important to synchrony (density-dependence, demographic and environmental stochasticity) and that these models are able to reproduce observed plant abundances [@Chu2015], perturbing the models reveals the processes responsible for the degree of species synchrony in our focal grassland communities.

THEORETICAL MODEL
-----------------
### The model
Our objective is to derive analytical predictions for species synchrony under special limiting cases that may or may not be realized in natural communities.
We constrain our focus to synchrony of per capita growth rates, rather than abundance, because growth rates represent the instantaneous response of species to the environment and competition, and are less susceptible to the legacy effects of drift and disturbance [@Loreau2008a].
Following @Loreau2008a and @DeMazancourt2013a, we define population growth, ignoring observation error, as

@@

#### Fitting statistical models
Vital rate regressions are the building blocks of our dynamic models: an integral projection model (IPM) and an individual-based model (IBM).
We followed the approach of @Chu2015 to fit statistical models for survival, growth, and recruitment.
We modeled survival probability of each genet as function of genet size, temporal variation among years, permanent spatial variation among groups of quadrats, and local neighborhood crowding from conspecific and heterospecific genets.
Regression coefficients for the effect of crowding by each species can be considered a matrix of interaction coefficients whose diagonals represent intraspecific interations and whose off-diagonals represent interspecific interactions [@Adler2010].
We modeled growth as the change in size of a genet from one year to the next, which depends on the same factors as the survival model.
We fit the survival and growth regressions using INLA [@Rue2014], a statistical package for fitting generalized linear mixed effects models via approximate Bayesian inference [@Rue2009], in R [@R2013].
Genet size and crowding were treated as fixed effects; spatial (quadrat groupings) and temporal (interannual) variation were treated as random effects on the intercept.

@@

#### Building dynamic multi-species models
Once we have fit the vital rate stastical models, building the population models is straightforward.
For the IBM, we initialize the model by randomly assigning plants spatial coordinates, sizes and species identities until each species achieves a density representative of that observed in the data.
We then project the model forward by using the survival regression to determine whether a genet lives or dies, the growth regression to calculate changes in genet size, and the recruitment regression to add new individuals that are distributed randomly in space.
Crowding is directly calculated at each time step since each genet is spatially referenced (just like the actual data).
Environmental stochasticity is not an inherent feature of IBMs, but is easily included since we fit year-specific temporal random effects for each vital rate regression.
Thus, to include temporal environmental variation, at each time step we randomly choose a set of estimated survival, growth, and recruitment parameters specific to one observation year.
For all simulations, we ignore the spatial random effect associated with variation among quadrat groups, so our simulations represent an average quadrat for each site.

The IPM is similar to the IBM in that it is built using the vital rate regressions [@Rees2009; @Rees2014], but it is different in that it is spatially-implicit and does not include demographic stochasticity.
Following @Chu2015, we use a mean field approximation that captures the essential features of spatial patterning to define the crowding index at each time step.
Temporal variation is included in exactly the same way as for the IBM.
For full details on the IPMs we use, see @Chu2015.

#### Simulation experiments
We performed removal simulation experiments where drivers (environmental stochasticity, demographic stochasticity, or interspecific competition) were removed one-by-one and combination.
To remove interspecific interactions, we set the off-diagonals of the interaction matrix for each vital rate regression to zero.
This retains intraspecific interactions, and thus density-dependence, and results in simulations where species are effectively growing in monoculture.
To remove the effect of a fluctuating environment, we removed the temporal (interannual) random effects from the regression equations.
To remove the effect of demographic stochasticity, we use the IPM rather than the IBM because the IPM does not include demographic stochasticity and demographic stochasticity cannot be removed from IBM simulations.
Since the effect of demographic stochasticity on population dynamics depends on population size [@Lande2003], we can control the strength of demographic stochasticity by simulating the IBM on different area sizes (e.g., plot sizes).
Note that the IPM must include environmental stochasticity because otherwise all populations go to a stable equilibrium, and the IBM must include demographic stochasticity because it explicitly models individual plants.

Using the above methods, we ran six simulation experiments:
(1) All drivers (environmental stochasticity, demographic stochasticity, or interspecific competition) present using the IBM;
(2) Demographic stochasticity removed using the IPM;
(3) Environmental stochastcity removed suing the IBM;
(4) Interspecific competition removed using the IBM;
(5) Interspecific competition and demographic stochasticity removed using the IPM; and
(6) Interspecific competition and environmental stochasticity removed using the IBM.
We ran IPM simulations for 2,000 time steps, after an initial 500 iteration burn-in period.
This allowed species time to reach their stable size distribution.
We then calculated the synchrony of species' per capita growth rates over 100 randomly selected contiguous 50 time-step sections.
We ran IBM simulations for 100 time steps, and repeated the simulations 100 times for each simulation experiment.
From those, we retained only the simulations in which no species went extinct due to demographic stochasticity.
Synchrony was calculated over the 100 time steps for each no extinction run within a model experiment.
To explore the effect of demographic stochasticity in different sized populations, we ran simulations (1) and (6) on plot sizes of 1, 2, 3, 4, and 5 square meters.

@@

### Results
Synchrony of species' per capita growth rates at our study sites ranged from 0.36 to 0.89 and synchrony of percent cover ranged from 0.15 to 0.92 (Table 2).
Synchrony tended to be higher in communities with few species (Arizona and New Mexico) and/or with relatively high temporal variability in percent cover (e.g., Montana).
Synchrony was lowest in Idaho, the only data set that includes two life forms: a shrub and three perennial grasses (Table 1).
For all five communities, species synchrony from IPM and IBM simulations closely approximated observed synchrony (Fig. X1), meaning that we can use the models to test the importance of different drivers of synchrony in these communities.
However, IBM-simulated synchrony is consistently, but only slightly, lower than IPM-simulated synchrony (Fig. X1), likely due to the desynchronizing effect of demographic stochasticity.

Across the five communities, our limiting case predictions closely matched synchrony from simulations designed to test each prediction (Table 3).
The correlation between our analytical predictions and simulated synchrony was 0.97 for $\phi_{R,\mathcal{M}_D}$ and 0.997 for $\phi_{R,\mathcal{M}_E}$.
The largest difference between predicted and simulated synchrony was 0.05 in New Mexico for $\phi_{R,\mathcal{M}_D}$ (Table 3).

Simulation experiments revealed that removing environmental fluctuations has the largest impact on synchrony, leading to a reduction in synchrony of species growth rates in four out five communities (Fig. 2).
Removing environmental fluctuations ("No E.S" simulations) decreased synchrony by 33% in Arizona, 48% in Kansas, 39% in Montana, and 40% in New Mexico.
Only in Idaho did removing environmental fluctuations cause an increase in synchrony (Fig. 2), but the effect was small (9% increase).
Species interactions are weak in these communities [Table SX and @Chu2015], so removing interspecific competition had little effect on synchrony (Fig. 2; "No Comp." simulations).
Removing competition caused, at most, a 5% change in synchrony (Table SX).
Removing demographic stochasticity ("No D.S." simulations) caused synchrony to increase slightly in all communities (Fig. 2), with an average 6% increase.
The desynchronizing effect of demographic stochasticity was able to modestly counteract the synchronizing force of the environment, but not enough to match the synchrony of species when only demographic stochasticity is operating (Fig. 3).
For all five communities, the synchrony of species' growth rates in monoculture was strongly associated with species synchrony in polyculture (rank correlation = 1; Fig. 3).
Results for synchrony of percent cover are qualitatively similar (Figs. SX-SX) but more noisy, as expected by theory [@Loreau2008a].

DISCUSSION
----------
Our study produced four main findings that were generally consistent across five natural plant communities: (1) limiting-case predictions from the theoretical model were well-supported by analagous simulations from the empirical models; (2) demographic stochasticity decreased community synchrony, as expected by theory, and its effect was largest in small populations; (3) environmental fluctuations increased community synchrony relative to simulations in constant environments because species-specific responses to the environment were positively, but not completely, correlated; and (4) interspecific interactions were weak and therefore had little impact on community synchrony.

### Simulations support theoretical predictions
Our theoretical predictions were derived from a relatively simple model of population dynamics and required several simplifying assumptions.
Yet, our theoretical predictions were strongly supported by our empirically-based model simulations of natural plant communities (Table 3).
Such a close match between our analytical predictions and the simulation results should inspire confidence in the ability of simple models to inform our understanding of species synchrony.
The theoretical population dynamical model we used here also successfully predicted ecosystem stability in several biodiversity-ecosystem function experiments [@DeMazancourt2013a].
Thus, there is accumulating evidence, now from experimental and observational studies, that the population dynamical approach is an extremely useful modeling framework for linking population dynamics to community and ecosystem level properties [@Loreau2010].

### Demographic stochasticity decreases synchrony
Demographic stochasticity is able to partially counteract the synchronizing effects of environmental fluctuations and interspecific interactions on per capita growth rates, but only when populations are small (Fig. 3), in agreement with theory [@Loreau2008a].
Even in small populations, however, demographic stochasticity is not a strong enough to completely counteract the synchronizing effects of environmental fluctuations and induce independent species fluctuations (Fig. 3).
These results confirm the theoretical argument by @Loreau2008a that independent fluctuations among interacting species in a non-constant environment should be rare.
Only in the Idaho community does synchrony of per capita growth rates approach independent fluctuations (1/*S*, where *S* is the number of specuies) in a non-constant environment (Fig. 3).
This is most likely due to the strong effect of demographic stochasticity on the shrub *Artemisia tripartita* since even a 5 $\text{m}^2$ quadrat would only contain a few individuals of that species.

### Environmental fluctuations drive community synchrony
In large populations where interspecific interactions are weak, synchrony is expected to be driven exclusively by environmental fluctuations (Equation 4).
Under such conditions community synchrony should approximately equal the synchrony of species' responses to the environment [@Loreau2008a].
Two lines of evidence lead us to conclude that environmental fluctuations drive species synchrony in our focal plant communities.
First, in our model simulations, removing interspecific interactions resulted in no discernable change in community-wide species synchrony of per capita growth rates (Fig. 2).
Second, removing environmental fluctuations from simulations consistently reduced synchrony (Fig. 2), and the synchrony of species in monoculture is a very strong predictor of synchrony of species in polyculture (Fig. 3).
Our results lead us to conclude that environmental fluctuations, not species interactions, are the primary driver of community-wide species synchrony.
Likewise, our results appear to be quite general: across four arid-to-subhumid grasslands community synchrony is almost soley due to environmental fluctuations since interspecific interactions are weak.
Only in the Idaho community did removing environmental fluctuations not cause a large decrease in synchrony, but removing competition had no effect either.
Given accumulating evidence that niche differences in natural communities are large [reviewed in @Chu2015], and thus species interactions are likely to be weak, our results may be general in natural plant communities.

The insensitivity of species synchrony to model perturbations in the Idaho community challenges the consistency of our results.
However, Idaho's outlier status is soley due to its functional diversity.
When we removed the shrub (*Artemisia tripartita*) from our analyses, results from the Idaho data set conformed with results from all other sites: removing environmental stochasticity caused a significant reduction in species synchrony (Fig. SX).
Our main results for Idaho (Fig. 2), with *A. tripartita* included, demonstrate how the processes that determine species synchrony interact in complex ways.
*A. tripartita* has a facilitative effect on each grass species across all vital rates, except for a small competitive effect on *H. comata*'s survival probability (Tables SX, SX, SX).
At the same time, all the perennial grasses have negative effects on each other for each vital rate (Tables SX, SX, SX).
We know synchrony is affected by interspecific competition [@Loreau2008a], but how facilitative effects manifest themselves is unknown.
The interaction of facilitation and competition is clearly capable of having a large effect on species synchrony, and future theoretical efforts should aim to include a wider range of species interactions.

A challenge to the generality of our results is that we were only able to model common, co-occuring species [see @Chu2015].
Rare species, which our analysis does not include, could be kept at low densities by competitive suppression due to strong interspecific interactions.
If we had been able to model rare species, we may have found a larger effect of competition on community synchrony.
However, rare species may occupy rare niches that do not overlap with other species, in which case synchrony would remain predominantly driven by environmental responses.
Rare species could also be limited by generalist natural enemies whose effects are density-independent but alter competitive hierarchies [@Mordecai2011].
Under such conditions, synchrony will depend on the degree of pathogen-induced fitness differences and the pathogen's response to environmental conditions.
Niether our model nor current theory explicitly considers the effects of pathogens on species synchrony, and this highlights the need for theoretical work on the interaction between mechanisms of species coexistence and mechanisms of species synchrony [@Loreau2010].

### Interspecific interactions had little impact on community synchrony
We expected community synchrony of per capita growth rates to decrease when we removed interspecific interactions [@Loreau2008a and Supplementary Information].
Contrary to expectations, community synchrony was virtually indistinguishable between simulations with and without interspecific interactions (Fig. 2).
The lack of an effect of interspecific competition on synchrony is in contrast to a large body of theoretical work that predicts a strong role for competition in creating compensatory dynamics [@Tilman1988] and a recent empirical analysis [@Gross2014].

Our results do not contradict the idea that competition can lead to compensatory dynamics, but they do highlight the fact that interspecific competition must be relatively strong to influence species synchrony.
The communities we analyzed are composed of species with very little niche overlap [@Chu2015] and weak interspecific interactions (Tables X1-X10).
Mechanistic consumer-resource models [@Lehman2000] and phenomenological Lotka-Volterra models [@Lehman2000; @Loreau2013] both confirm that the effect of competition on species synchrony diminishes as niche overlap increases.
In that sense, our results are not surprising: interspecific interactions are weak, so of course removing them does not affect synchrony.
More surprising is that our focal communities have little niche overlap. 
But, as discussed by @Chu2015, little niche overlap becomes less surprising when we consider the virtually limitless niche axes upon which species can partition themselves [@Clark2010].

>>>>

\begin{abstract}
Temporal asynchrony among species is an important mechanism through which diversity can stabilize ecosystem function, but identifying the mechanisms that determine synchrony remains a challenge.
Here, we refine and test theory showing that synchrony depends on three factors: species responses to environmental variation, interspecific competition, and demographic stochasticity. We then conduct simulation experiments with empirical population models to quantify the relative importance of these factors in five plant communities.
In all five communities, theoretical predictions closely matched simulated synchrony for the limiting cases where only demographic stochasticity or environmental variation are present, meaning that theory developed with simple models also applies to our empirical models.
Simulations experiments showed that the average synchrony of per capita growth rates, which can range from 0 (perfect asynchrony) to 1 (perfect synchrony), was higher when environmental variation was present (0.62) rather than absent (0.43).
Removing interspecific competition and demographic stochasticity had small effects on synchrony. In these plant communities, where species interactions and demographic stochasticity have little influence, synchrony reflects the covariance in species responses to the environment.
\end{abstract}

@@

INTRODUCTION
------------
Ecosystems are being transformed by species extinctions [@Cardinale2012], changes in community composition [@Dornelas2014a; @Vellend2013], and anthropogenic environmental change [@Vitousek1997], impacting the provisioning and stability of ecosystem services [@Loreau2001a; @Hooper2005; @Rockstrom2009].
Experiments have provided compelling evidence that decreases in species richness will decrease productivity [@Tilman2001] and the temporal stability of productivity [@Tilman2006; @Hector2010].
The stabilizing effect of species richness stems from individual species fluctuating asynchronously through time [@Hector2010; @Isbell2009; @DeMazancourt2013a].
Species richness affects synchrony because larger species pools are more likely to contain species that respond disimilarly to environmental conditions [@Yachi1999], implying that species losses will reduce ecosystem stability.
Even without species losses, abiotic homogenization can weaken compensatory dynamics and, in turn, decrease temporal stability of ecosystem function [@Hautier2014].
Predicting the impacts of global change requires a mechanistic understanding of species synchrony in natural settings.

Theory identifies the three main determinants of species synchrony as environmental stochasticity, demographic stochasticity, and interspecific competition [@Loreau2008a; @Gonzalez2009; @Loreau2013].
For example, in a community composed of large (no demographic stochasticity) and weakly interacting (no interspecific competition) populations, community-wide species synchrony should be determined by the covariance of species' responses to the environment [@Loreau2008a].
However, such a prediction relies on a relatively simple population model and only holds under two assumptions: (i) species' responses to the environment are similar in magnitude and (ii) all species have similar growth rates.
Whether such theoretical predictions hold in natural communities where species differences are unlikely to be symmetrical remains unkown: no study has explicitly tested theory on the drivers of species synchrony in natural communities.

@@

The best way to quantify the effects of environmental stochasticity, demographic stochasticity, and interspecific competition is to remove them one-by-one, and in combination.
In principle, this could be done experimentally, but empirically-based models of interacting populations, fit with data sets from natural communities, offer a practical alternative.
For example, @Mutshinda2009 fit a dynamic population model to several community time series of insect and bird abundances.
They used a statistical technique to decompose temporal variation into competition and environmental components, and found that postively correlated environmental responses among species determined community dynamics.
While a major step forward, Mutshinda et al.'s (2009) modeling technique relied on abundance data that may or may not reliably capture competitive interactions that occur at the individual level.
Furthermore, although @Mutshinda2009 quantified the relative importance of environmental stochasticity and competition to explain the observed variation of species synchrony, they did not use the model to quantify how much synchrony would change when each factor is removed.

Here, we use multi-species population models fit to long-term demographic data from five semi-arid plant communities to test theory on the drivers of species synchrony.
Our objectives are to (1) derive and test theoretical predictions of species synchrony and (2) determine the relative influence of environmental stochasticity, demographic stochasticity, and interspecific competition on species synchrony in natural plant communities.
To achieve these objectives, we first refine theory that has been used to predict the effects of species richness on ecosystem stability [@DeMazancourt2013a] and species synchrony [@Loreau2008a] to generate predictions of community-wide species synchrony under two limiting cases derived from the dynamics of individual species in monoculture.
We then confront our theoretical predictions with simulations from the empirically-based population models.
Second, we use the multi-species population models to perform simulation experiments that isolate the effects of environmental stochasticity, demographic stochasticity, and interspecific competition on community-wide species synchrony.
Given that our population models capture the essential features of community dynamics important to synchrony (density-dependence, and demographic and environmental stochasticity), and that these models successfully reproduce observed community dynamics [@Chu2015], perturbing the models can reveal the processes that determine species synchrony in our focal grassland communities.

THEORETICAL MODEL
-----------------
### The model
While existing theory has identified the factors driving synchrony, we do not have a simple expression to predict synchrony in a particular community with all factors operating simultaneously. However, we can derive analytical predictions for species synchrony under special limiting cases. 
We constrain our focus to synchrony of per capita growth rates, rather than abundances, because growth rates represent the instantaneous response of species to the environment and competition, and are less susceptible to the legacy effects of drift and disturbance [@Loreau2008a].
Following @Loreau2008a and @DeMazancourt2013a, we define population growth, ignoring observation error, as

@@

#### Fitting statistical models
Vital rate regressions are the building blocks of our dynamic models: an integral projection model (IPM) and an individual-based model (IBM).
We followed the approach of @Chu2015 to fit statistical models for survival, growth, and recruitment.
We modeled survival probability of each genet as function of genet size, temporal variation among years, permanent spatial variation among groups of quadrats, and local neighborhood crowding from conspecific and heterospecific genets.
Regression coefficients for the effect of crowding by each species can be considered a matrix of interaction coefficients whose diagonals represent intraspecific interations and whose off-diagonals represent interspecific interactions [@Adler2010]. These interaction coefficients can take positive (facilitative) or negative (competitive) values.
We modeled growth as the change in size of a genet from one year to the next, which depends on the same factors as the survival model.
We fit the survival and growth regressions using INLA [@Rue2014], a statistical package for fitting generalized linear mixed effects models via approximate Bayesian inference [@Rue2009], in R [@R2013].
Genet size and crowding were treated as fixed effects; spatial (quadrat groupings) and temporal (interannual) variation were treated as random effects on the intercept.

@@

#### Building dynamic multi-species models
Once we have fit the vital rate stastical models, building the population models is straightforward.
For the IBM, we initialize the model by randomly assigning plants spatial coordinates, sizes and species identities until each species achieves a density representative of that observed in the data.
We then project the model forward by using the survival regression to determine whether a genet lives or dies, the growth regression to calculate changes in genet size, and the recruitment regression to add new individuals that are distributed randomly in space.
Crowding is directly calculated at each time step since each genet is spatially referenced (as in the observed data).
Environmental stochasticity is not an inherent feature of IBMs, but is easily included since we fit year-specific temporal random effects for each vital rate regression.
To include temporal environmental variation, at each time step we randomly choose a set of estimated survival, growth, and recruitment parameters specific to one observation year.
For all simulations, we ignore the spatial random effect associated with variation among quadrat groups, so our simulations represent an average quadrat for each site.

The IPM uses the same vital rate regressions as the IBM [@Rees2009; @Rees2014], but it is spatially-implicit and does not include demographic stochasticity.
Following @Chu2015, we use a mean field approximation that captures the essential features of spatial patterning to define the crowding index at each time step.
Temporal variation is included in exactly the same way as for the IBM.
For full details on the IPMs we use, see @Chu2015.

#### Simulation experiments
We performed removal simulation experiments where drivers (environmental stochasticity, demographic stochasticity, or interspecific competition) were removed one-by-one and in combination.
To remove interspecific interactions, we set the off-diagonals of the interaction matrix for each vital rate regression to zero.
This retains intraspecific interactions, and thus density-dependence, and results in simulations where species are effectively growing in monoculture.
To remove the effect of a fluctuating environment, we removed the temporal (interannual) random effects from the regression equations.
To remove the effect of demographic stochasticity, we use the IPM rather than the IBM because the IPM does not include demographic stochasticity (demographic stochasticity cannot be removed from the IBM).
Since the effect of demographic stochasticity on population dynamics depends on population size [@Lande2003], we can control the strength of demographic stochasticity by simulating the IBM on areas (e.g. plots) of different size.

We conducted the following six simulation experiments:
(1) IBM: All drivers (environmental stochasticity, demographic stochasticity, or interspecific competition) present;
(2) IPM: Demographic stochasticity removed;
(3) IBM: Environmental stochastcity removed;
(4) IBM: Interspecific competition removed;
(5) IPM: Interspecific competition and demographic stochasticity removed;
(6) IBM: Interspecific competition and environmental stochasticity removed.
We ran IPM simulations for 2,000 time steps, after an initial 500 iteration burn-in period.
This allowed species time to reach their stable size distribution.
We then calculated the synchrony of species' per capita growth rates over 100 randomly selected contiguous 50 time-step sections.
We ran IBM simulations for 100 time steps, and repeated the simulations 100 times for each simulation experiment.
From those, we retained only the simulations in which no species went extinct due to demographic stochasticity.
Synchrony was calculated over the 100 time steps for each no extinction run within a model experiment.
To explore the effect of demographic stochasticity in different sized populations, we ran simulations (1) and (6) on plot sizes of 1, 2, 3, 4, and 5 square meters.

@@

### Results
Synchrony of species' per capita growth rates at our study sites ranged from 0.36 to 0.89 and synchrony of percent cover ranged from 0.15 to 0.92 (Table 2).
Synchrony tended to be higher in communities with few species (Arizona and New Mexico) and/or with relatively high temporal variability in percent cover (e.g., Montana).
Synchrony was lowest in Idaho, the only data set that includes two life forms: a shrub and three perennial grasses (Table 1).
For all five communities, species synchrony from IPM and IBM simulations closely approximated observed synchrony (Fig. X1).
IBM-simulated synchrony is consistently, but only slightly, lower than IPM-simulated synchrony (Fig. X1), likely due to the desynchronizing effect of demographic stochasticity.

Across the five communities, our limiting case predictions closely matched synchrony from the corresponding simulation experiment (Table 3).
The correlation between our analytical predictions and simulated synchrony was 0.97 for $\phi_{R,\mathcal{M}_D}$ and 0.997 for $\phi_{R,\mathcal{M}_E}$.
The largest difference between predicted and simulated synchrony was 0.05 in New Mexico for $\phi_{R,\mathcal{M}_D}$ (Table 3).

Simulation experiments revealed that removing environmental fluctuations has the largest impact on synchrony, leading to a reduction in synchrony of species growth rates in four out five communities (Fig. 2).
Removing environmental fluctuations ("No E.S" simulations) decreased synchrony by 33% in Arizona, 48% in Kansas, 39% in Montana, and 40% in New Mexico.
Only in Idaho did removing environmental fluctuations cause an increase in synchrony (Fig. 2), but the effect was small (9% increase).
Species interactions are weak in these communities [Table SX and @Chu2015], and removing interspecific competition had little effect on synchrony (Fig. 2; "No Comp." simulations).
Removing competition caused, at most, a 5% change in synchrony (Table SX).
Removing demographic stochasticity ("No D.S." simulations) caused synchrony to increase slightly in all communities (Fig. 2), with an average 6% increase [IS THIS FOR THE SMALLEST SIMULATED PLOT SIZE?].
The desynchronizing effect of demographic stochasticity modestly counteracted the synchronizing force of the environment, but not enough to lower synchrony to the level observed when only demographic stochasticity is operating (Fig. 3).
For all five communities, the synchrony of species' growth rates in monoculture was strongly associated with species synchrony in polyculture (rank correlation = 1; Fig. 3).
Results for synchrony of percent cover are qualitatively similar (Figs. SX-SX) but more variable, as expected by theory [@Loreau2008a].

DISCUSSION
----------
Our study produced four main findings that were generally consistent across five natural plant communities: (1) limiting-case predictions from the theoretical model were well-supported by simulations from the empirical models; (2) demographic stochasticity decreased community synchrony, as expected by theory, and its effect was largest in small populations; (3) environmental fluctuations increased community synchrony relative to simulations in constant environments because species-specific responses to the environment were positively, though not perfectly, correlated; and (4) interspecific interactions were weak and therefore had little impact on community synchrony.

### Simulations support theoretical predictions
Our theoretical predictions were derived from a simple model of population dynamics and required several simplifying assumptions, raising questions about their relevance to natural communities.
However, the theoretical predictions were strongly supported by simulations of population models fit to long-term data from natural plant communities (Table 3).
Such a close match between our analytical predictions and the simulation results should inspire confidence in the ability of simple models to inform our understanding of species synchrony.
The theoretical population dynamical model we used here also successfully predicted ecosystem stability in several biodiversity-ecosystem function experiments [@DeMazancourt2013a].
The accumulating evidence from both experimental and observational studies demonstrates the utility of linking population dynamics to community and ecosystem level properties [@Loreau2010]. [THIS LAST SENTENCE SUCKS]

### Demographic stochasticity decreases synchrony
Demographic stochasticity partially counteracted the synchronizing effects of environmental fluctuations and interspecific interactions on per capita growth rates, but only when populations were small (Fig. 3), in agreement with theory [@Loreau2008a].
Even in small populations, however, demographic stochasticity was not strong enough to completely counteract the synchronizing effects of environmental fluctuations and induce independent species fluctuations (Fig. 3).
These results confirm the theoretical argument by @Loreau2008a that independent fluctuations among interacting species in a non-constant environment should be rare.
Only in the Idaho community does synchrony of per capita growth rates approach independent fluctuations (1/*S*, where *S* is the number of specuies) in a non-constant environment (Fig. 3).
This is most likely due to the strong effect of demographic stochasticity on the shrub *Artemisia tripartita* since even a 5 $\text{m}^2$ quadrat would only contain a few individuals of that species.

### Environmental fluctuations drive community synchrony
In large populations where interspecific interactions are weak, synchrony is expected to be driven exclusively by environmental fluctuations (Equation 4).
Under such conditions community synchrony should approximately equal the synchrony of species' responses to the environment [@Loreau2008a].
Two lines of evidence lead us to conclude that environmental fluctuations drive species synchrony in our focal plant communities.
First, in our simulation experiments, removing interspecific interactions resulted in no discernible change in community-wide species synchrony of per capita growth rates (Fig. 2).
Second, removing environmental fluctuations from simulations consistently reduced synchrony (Fig. 2), and the synchrony of species in monoculture was a very strong predictor of synchrony of species in polyculture (Fig. 3).
Our results lead us to conclude that environmental fluctuations, not species interactions, are the primary driver of community-wide species synchrony in the communities we studied.
Given accumulating evidence that niche differences in natural communities are large [reviewed in @Chu2015], and thus species interactions are likely to be weak, our results may be general in natural plant communities.

In the Idaho community, removing environmental fluctuations did not cause a large decrease in synchrony.
However, that result appears to be an artifact. Removing environmental variation results in a negative invasion growth rate for *A. tripartita*. Although we only analyzed IBM runs in which *A. tripartita* had not yet gone extinct, it was at much lower abundance than in the other simulation runs.
When we removed the shrub (*Artemisia tripartita*) from all simulations, the Idaho results conformed with results from all other sites: removing environmental stochasticity caused a significant reduction in species synchrony (Fig. SX).
Our main results for Idaho (Fig. 2), with *A. tripartita* included, demonstrate how the processes that determine species synchrony interact in complex ways.
*A. tripartita* has a facilitative effect on each grass species across all vital rates, except for a small competitive effect on *H. comata*'s survival probability (Tables SX, SX, SX).
At the same time, all the perennial grasses have negative effects on each other for each vital rate (Tables SX, SX, SX).
We know synchrony is affected by interspecific competition [@Loreau2008a], but how facilitative effects manifest themselves is unknown.
The interaction of facilitation and competition is clearly capable of having a large effect on species synchrony, and future theoretical efforts should aim to include a wider range of species interactions.

A challenge to the generality of our results is that we were only able to model common, co-occuring species [see @Chu2015].
Rare species, which our analysis does not include, could be kept at low densities by competitive suppression due to strong interspecific interactions.
If we had been able to model rare species, we may have found a larger effect of competition on community synchrony.
However, rare species may occupy rare niches that do not overlap with other species, in which case synchrony would remain predominantly driven by environmental responses.
Rare species could also be limited by generalist natural enemies whose effects are density-independent but alter competitive hierarchies [@Mordecai2011].
Under such conditions, synchrony will depend on the degree of pathogen-induced fitness differences and the pathogen's response to environmental conditions.
Neither our model nor current theory explicitly considers the effects of pathogens on species synchrony, and this highlights the need for theoretical work on the interaction between mechanisms of species coexistence and mechanisms of species synchrony [@Loreau2010].

### Interspecific interactions had little impact on community synchrony
We expected community synchrony of per capita growth rates to decrease when we removed interspecific interactions [@Loreau2008a and Supplementary Information].
We found that community synchrony was virtually indistinguishable between simulations with and without interspecific interactions (Fig. 2).
The lack of an effect of interspecific competition on synchrony is in contrast to a large body of theoretical work that predicts a strong role for competition in creating compensatory dynamics [@Tilman1988] and a recent empirical analysis [@Gross2014].

Our results do not contradict the idea that competition can lead to compensatory dynamics, but they do highlight the fact that interspecific competition must be relatively strong to influence species synchrony.
The communities we analyzed are composed of species with very little niche overlap [@Chu2015] and weak interspecific interactions (Tables X1-X10).
Mechanistic consumer-resource models [@Lehman2000] and phenomenological Lotka-Volterra models [@Lehman2000; @Loreau2013] both confirm that the effect of competition on species synchrony diminishes as niche overlap increases.
In that sense, our results are not surprising: interspecific interactions are weak, so of course removing them does not affect synchrony.
